### 2016-06-03 w-wires/paper_gerasimovda.tex
Finished the proof!

To estimate, we will split the integration in two parts: from $Z$ to $C$ and from $C$ to $R + C$.

First part:
\begin{align*} 
    & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + Z)}} \frac{1}{\sqrt{(R + C - C)}} dy\\
=   & \frac{1}{\sqrt{R - C + Z}} \frac{R}{\sqrt{R}}  \int\limits_{y = Z}^{C} \ln^2 f(y) \frac{1}{R^2 - C^2 + 2 C y} dy\\
\end{align*}

\todo{ugh, estimate via $\int \ln^2(a x + b) \frac{1}{c x + d}$? }

Second part:

\begin{align*}
    & \int\limits_{y = C}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\le & \int\limits_{y = C}^{R + C} \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 C C} \frac{1}{\sqrt{(R - C + C)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
=   & \ln^2 f(C) \frac{R}{R^2 + C^2} \frac{1}{\sqrt{R}} \int\limits_{y = C}^{R + C} \frac{1}{\sqrt{R + C - y}} dy\\
=   & \ln^2 f(C) \frac{R}{R^2 + C^2} \frac{1}{\sqrt{R}} 2 \sqrt{R}\\
\end{align*}
\todo{show that logarithmic part is constant, that finishes the proof}

>>>>

\subsection*{Second part, from $Z + \frac{1}{R}$ to $C$}

\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(Z + \frac{1}{R}) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - C}} \frac{1}{\sqrt{R - C + Z}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

\todo{Essentially, we have to integrate blah-blah}. We use well known integral:

\[
\int \frac{1}{a x + b} = \frac{\ln (a x + b)}{a}
\]
, in our case $a = 2 (C + 1)$, $b = R^2 - C^2 + 1$. By applying the \todo{fundamental theorem?} over the second interval, we get:

\[
\frac{\ln \frac{2 (C + 1) C + R^2 - C^2 + 1}{2 (C + 1) (Z + \frac{1}{R}) + R^2 - C^2 + 1}}{2 (C + 1)} = \frac{\mcO(\ln(C^2 + R^2)) + \mcO(TODO)}{C + 1}
\]

\todo{We should probably estimate logarithm at zero by a hyperbola after that. Finish the proof.}

\subsection*{Third part, from $C$ to $C + R$}

\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

Integral of $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is trivial and equals to $2 \sqrt{R}$.

\todo{Simplify, it's clear that integral goes to zero}
